---
title: "30DaysMapChallenge"
author: "Kuma Luo"
date: "2024-11-14"
output: html_document
---
```{r}
library(tidycensus)
library(tidyverse)
library(ggbeeswarm)
library(scales)
library(ggiraph)  
library(scales)   
library(tigris)   
```

# 11/13 Day 03 Polygon

```{r}
us_income <- get_acs(
  geography = "state",          
  variables = "B19013_001",    
  year = 2019,                 
  survey = "acs1",             
  geometry = TRUE,             
  resolution = "20m"           
)

us_income_shifted <- us_income %>%
  shift_geometry(position = "outside") %>%  
  mutate(tooltip = paste(NAME, dollar(estimate), sep = ": "))  

gg_income <- ggplot(us_income_shifted, aes(fill = estimate)) +
  geom_sf_interactive(aes(tooltip = tooltip, data_id = NAME),  
                      size = 0.1) +  
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", labels = label_dollar()) + 
  labs(
    title = "Median household income by State, 2019",  
    caption = "Data source: 2019 1-year ACS, US Census Bureau",  
    fill = "ACS estimate" 
  ) +
  theme_void()  

girafe(ggobj = gg_income) %>%
  girafe_options(
    opts_hover(css = "fill:cyan;"),  
    opts_zoom(max = 10)  
  )
```

Green was chosen for income to convey growth and prosperity, common associations with financial metrics. The legend shows dollar values for clarity, and the clean design, with minimal distractions, directs viewers' attention to geographic patterns in income distribution across the states. Also, this interactive map could provide detailed value of each state when you click the state you want to check the income value.


# 11/14 Day 01 Points

```{r}
library(sf)
library(ggplot2)
library(tigris)
install.packages("ggspatial")
library(ggspatial) 
library(ggrepel)
library(dplyr)
```


```{r}

stations <- st_read("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/Highspeed_Stations/Highspeed_Stations.shp")

key_station_names <- c(
  "30th Street Station", "69th Street Transportation Center", "Frankford Transportation Center",
  "Norristown Transportation Center", "Fern Rock Transportation Center", "Arrott Transportation Center",
  "NRG Station", "Chinatown", "8th", "Olney", "Girard", "Wynnewood Rd", "Ardmore Ave", 
  "Bryn Mawr", "Villanova"
)

key_stations <- stations %>%
  filter(Station %in% key_station_names) 

se_pa_counties <- counties(state = "PA", cb = TRUE, year = 2021) %>%
  filter(NAME %in% c("Delaware", "Montgomery", "Philadelphia")) %>%
  st_transform(st_crs(stations)) 

ggplot() +
  geom_sf(data = se_pa_counties, fill = "grey90", color = "black", size = 0.5) +
  geom_sf(data = stations, color = "blue", size = 1, alpha = 0.5) +  
  geom_sf(data = key_stations, color = "red", size = 3) +  
  geom_label_repel(data = key_stations, aes(geometry = geometry, label = Station), 
                   stat = "sf_coordinates", nudge_y = 0.01, color = "darkred",
                   size = 3, min.segment.length = 0) +  
  labs(
    title = "Key High-Speed and Major Stations in in Southeastern Pennsylvania",
    caption = "Data source: SEPTA"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.caption = element_text(size = 10)
  )

```

This map highlights the key high-speed and major rail stations in Southeastern Pennsylvania, focusing on Philadelphia and its surrounding counties (Delaware, and Montgomery). The highlighted stations represent critical transit hubs and high-traffic stops, providing an overview of the region’s significant rail nodes. Key stations are marked with larger, red points to distinguish them from other stations, which are represented with smaller blue dots. Each highlighted station is labeled with a clear, bordered label, using ggrepel to prevent overlap and ensure readability. 


# 11/15 Day 02 Line

```{r}
hydro_features <- st_read("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/Hydrographic_Features_Arc/Hydrographic_Features_Arc.shp")

```

```{r}
highlighted_features <- c("Schuylkill River", "Delaware River")

highlighted_hydro <- hydro_features %>%
  filter(creek_name %in% highlighted_features)

highlighted_labels <- highlighted_hydro %>%
  group_by(creek_name) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup()
```

```{r}
ggplot() +
  geom_sf(data = se_pa_counties, fill = "grey95", color = "grey", size = 0.3, alpha = 0.5) +  
  geom_sf(data = hydro_features, color = "lightblue", size = 0.5) +               
  geom_sf(data = highlighted_hydro, color = "blue", size = 1.2) +                  
  geom_label_repel(data = highlighted_labels, aes(geometry = geometry, label = creek_name), 
                   stat = "sf_coordinates", nudge_y = 0.01, color = "darkblue",
                   size = 3.5, min.segment.length = 0) +                           
  labs(
    title = "Hydrographic Features in Philadelphia",
    subtitle = "Highlighted rivers and waterways",
    caption = "Data source: OpenDataPhilly"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14, face = "italic"),
    plot.caption = element_text(size = 10)
  )
```

This map visualizes the hydrographic network in Philadelphia, focusing specifically on the prominent waterways: the Delaware River and Schuylkill River. All hydrographic features in the city are displayed in a light blue to provide a contextual background, while the highlighted rivers are represented in a more vivid blue and labeled for clarity. By emphasizing the Delaware and Schuylkill Rivers, the map emphasizes the importance of these waterways to the city’s geography and infrastructure. This design allows viewers to quickly identify these key rivers, while still appreciating the complexity of Philadelphia's overall hydrographic system.







