---
title: "30DaysMapChallenge"
author: "Kuma Luo"
date: "2024-11-14"
output: html_document
---
```{r}
library(tidycensus)
library(tidyverse)
library(ggbeeswarm)
library(scales)
library(ggiraph)  
library(scales)   
library(tigris)   
```

# 11/13 Day 03 Polygon

```{r}
us_income <- get_acs(
  geography = "state",          
  variables = "B19013_001",    
  year = 2019,                 
  survey = "acs1",             
  geometry = TRUE,             
  resolution = "20m"           
)

us_income_shifted <- us_income %>%
  shift_geometry(position = "outside") %>%  
  mutate(tooltip = paste(NAME, dollar(estimate), sep = ": "))  

gg_income <- ggplot(us_income_shifted, aes(fill = estimate)) +
  geom_sf_interactive(aes(tooltip = tooltip, data_id = NAME),  
                      size = 0.1) +  
  scale_fill_gradient(low = "lightgreen", high = "darkgreen", labels = label_dollar()) + 
  labs(
    title = "Median household income by State, 2019",  
    caption = "Data source: 2019 1-year ACS, US Census Bureau",  
    fill = "ACS estimate" 
  ) +
  theme_void()  

girafe(ggobj = gg_income) %>%
  girafe_options(
    opts_hover(css = "fill:cyan;"),  
    opts_zoom(max = 10)  
  )
```

Green was chosen for income to convey growth and prosperity, common associations with financial metrics. The legend shows dollar values for clarity, and the clean design, with minimal distractions, directs viewers' attention to geographic patterns in income distribution across the states. Also, this interactive map could provide detailed value of each state when you click the state you want to check the income value.


# 11/14 Day 01 Points

```{r}
library(sf)
library(ggplot2)
library(tigris)
install.packages("ggspatial")
library(ggspatial) 
library(ggrepel)
library(dplyr)
```


```{r}

stations <- st_read("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/Highspeed_Stations/Highspeed_Stations.shp")

key_station_names <- c(
  "30th Street Station", "69th Street Transportation Center", "Frankford Transportation Center",
  "Norristown Transportation Center", "Fern Rock Transportation Center", "Arrott Transportation Center",
  "NRG Station", "Chinatown", "8th", "Olney", "Girard", "Wynnewood Rd", "Ardmore Ave", 
  "Bryn Mawr", "Villanova"
)

key_stations <- stations %>%
  filter(Station %in% key_station_names) 

se_pa_counties <- counties(state = "PA", cb = TRUE, year = 2021) %>%
  filter(NAME %in% c("Delaware", "Montgomery", "Philadelphia")) %>%
  st_transform(st_crs(stations)) 

ggplot() +
  geom_sf(data = se_pa_counties, fill = "grey90", color = "black", size = 0.5) +
  geom_sf(data = stations, color = "blue", size = 1, alpha = 0.5) +  
  geom_sf(data = key_stations, color = "red", size = 3) +  
  geom_label_repel(data = key_stations, aes(geometry = geometry, label = Station), 
                   stat = "sf_coordinates", nudge_y = 0.01, color = "darkred",
                   size = 3, min.segment.length = 0) +  
  labs(
    title = "Key High-Speed and Major Stations in in Southeastern Pennsylvania",
    caption = "Data source: SEPTA"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.caption = element_text(size = 10)
  )

```

This map highlights the key high-speed and major rail stations in Southeastern Pennsylvania, focusing on Philadelphia and its surrounding counties (Delaware, and Montgomery). The highlighted stations represent critical transit hubs and high-traffic stops, providing an overview of the region’s significant rail nodes. Key stations are marked with larger, red points to distinguish them from other stations, which are represented with smaller blue dots. Each highlighted station is labeled with a clear, bordered label, using ggrepel to prevent overlap and ensure readability. 


# 11/15 Day 02 Line

```{r}
hydro_features <- st_read("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/Hydrographic_Features_Arc/Hydrographic_Features_Arc.shp")

```

```{r}
highlighted_features <- c("Schuylkill River", "Delaware River")

highlighted_hydro <- hydro_features %>%
  filter(creek_name %in% highlighted_features)

highlighted_labels <- highlighted_hydro %>%
  group_by(creek_name) %>%
  summarize(geometry = st_union(geometry)) %>%
  ungroup()
```

```{r}
ggplot() +
  geom_sf(data = se_pa_counties, fill = "grey95", color = "grey", size = 0.3, alpha = 0.5) +  
  geom_sf(data = hydro_features, color = "lightblue", size = 0.5) +               
  geom_sf(data = highlighted_hydro, color = "blue", size = 1.2) +                  
  geom_label_repel(data = highlighted_labels, aes(geometry = geometry, label = creek_name), 
                   stat = "sf_coordinates", nudge_y = 0.01, color = "darkblue",
                   size = 3.5, min.segment.length = 0) +                           
  labs(
    title = "Hydrographic Features in Philadelphia",
    subtitle = "Highlighted rivers and waterways",
    caption = "Data source: OpenDataPhilly"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14, face = "italic"),
    plot.caption = element_text(size = 10)
  )
```

This map visualizes the hydrographic network in Philadelphia, focusing specifically on the prominent waterways: the Delaware River and Schuylkill River. All hydrographic features in the city are displayed in a light blue to provide a contextual background, while the highlighted rivers are represented in a more vivid blue and labeled for clarity. By emphasizing the Delaware and Schuylkill Rivers, the map emphasizes the importance of these waterways to the city’s geography and infrastructure. This design allows viewers to quickly identify these key rivers, while still appreciating the complexity of Philadelphia's overall hydrographic system.


# 11/16 Day 16 Choropleth
```{r}
planning_districts <- st_read("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge//Vital_Natality_PD/Vital_Natality_PD.shp")

planning_districts_filtered <- planning_districts %>%
  filter(YEAR == 2023, METRIC_NAM == "count_births")

```

```{r}
ggplot(planning_districts_filtered) +
  geom_sf(aes(fill = METRIC_VAL), color = "white", size = 0.3) +
  scale_fill_viridis_c(
    option = "magma", direction = -1,
    name = "Number of Births",
    labels = comma
  ) +
  annotate(
    "text", x = -75.10, y = 39.85, label = "Lowest Births Here", 
    color = "red", size = 4, fontface = "bold"
  ) +
  annotate(
    "segment", x = -75.18, xend = -75.15, y = 39.9, yend = 39.85, 
    color = "red"
  ) +
  labs(
    title = "Philadelphia Vital Statistics - Natality (Births in 2023)",
    subtitle = "Number of births by planning district",
    caption = "Data source: OpenDataPhilly"
  ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14, face = "italic"),
    plot.caption = element_text(size = 10),
    legend.position = "right"
  )
```

This choropleth map visualizes the number of births by planning district in Philadelphia for the year 2023. Each planning district is colored based on the total number of births, with darker shades indicating higher birth counts and lighter shades indicating lower birth counts. An annotation highlights the planning district with the lowest number of births. The goal of this map is to provide a clear and visually engaging way to understand natality trends across Philadelphia's planning districts. By highlighting the lowest birth area, I want to form a narrative element, and inspire more public health, urban planning, or policy-making discussions.

# 11/17 Day 07 Vintage Style

```{r}
install.packages("showtext")
library(showtext)
install.packages("ggtext")
library(ggtext)


landmarks <- st_read("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/Landmarks_AGOTrainingOnly-shp/8902d0d9-94eb-4763-a5e7-7dc4e412475a2020329-1-xj0ntw.uct4l.shp")

museums <- landmarks %>%
  filter(FEAT_TYPE == "Museum")

showtext_auto()
font_add_google(name = "IM Fell English", family = "vintage")

```
```{r}
museums_points <- museums %>%
  st_centroid()
```
```{r}
install.packages("ggimage")
library(ggimage)

```

```{r}
museum_icon <- "/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/MuseumIcon.png"

```


```{r}
ggplot() +
  geom_sf(data = landmarks, fill = "grey", color = NA, size = 0.1, alpha = 0.3) +
  geom_image(
    data = museums_points, 
    aes(x = st_coordinates(geometry)[, 1], y = st_coordinates(geometry)[, 2], image = museum_icon),
    size = 0.02  
  ) +
  labs(
    title = "<span style='font-size:16pt; font-family:vintage;'>Philadelphia Museums</span>",
    subtitle = "<span style='font-size:12pt; font-family:vintage;'>Distribution of Museums in the City</span>",
    caption = "Data source: OpenDataPhilly",
    x = NULL,  
    y = NULL  
    ) +
  theme_minimal(base_family = "vintage") +
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.background = element_rect(fill = "#F6F0E4", color = NA), 
    plot.background = element_rect(fill = "#F6F0E4", color = NA, size = 1), 
    panel.grid = element_blank(),
    legend.position = "none", 
    plot.title = element_markdown(hjust = 0.5, margin = margin(b = 10)),
    plot.subtitle = element_markdown(hjust = 0.5, margin = margin(b = 20)),
    plot.caption = element_text(hjust = 0.5, face = "italic", size = 10, margin = margin(t = 20))
  )
```

The IM Fell English font was chosen to evoke a classic, historical feel suitable for a map focusing on cultural landmarks like museums. A sepia-toned background (#F6F0E4) and muted black frame give the map a vintage and timeless appearance. The goal was to create a visually striking map that communicates the cultural richness of Philadelphia through its museums while adhering to the vintage theme. 

# 11/18 Day 04 Hexagons

```{r}
crime_data <- read.csv("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/crime_incidents_philly.csv")

theft_data <- crime_data %>%
  filter(!is.na(lat) & !is.na(lng) & text_general_code == "Thefts")

theft_sf <- st_as_sf(theft_data, coords = c("lng", "lat"), crs = 4326)

theft_sf <- st_transform(theft_sf, crs = 3857)

```

```{r}
valid_x_min <- -75.3  
valid_x_max <- -74.9  
valid_y_min <- 39.8   
valid_y_max <- 40.2

theft_sf_filtered <- theft_sf %>%
  filter(
    point_x != 0 & point_y != 0,  
    point_x >= valid_x_min & point_x <= valid_x_max,  
    point_y >= valid_y_min & point_y <= valid_y_max   
  )
```


```{r}

ggplot() +
  stat_bin_hex(
    data = theft_sf_filtered,
    aes(x = point_x, y = point_y), 
    bins = 30          
  ) +
  scale_fill_viridis_c(option = "inferno", name = "Theft Density", direction = -1) +
  geom_label(
    aes(x = -75.11, y = 39.95, label = "High Theft Area"), 
    fill = "white", color = "red", fontface = "bold", size = 4
  ) +
  labs(
    title = "Philadelphia Theft Incidents",
    subtitle = "Density of theft incidents aggregated into hexagonal bins",
    caption = "Data source: OpenDataPhilly"
  ) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14, face = "italic"),
    plot.caption = element_text(size = 10)
  )

```

This map visualizes the density of theft incidents in Philadelphia, by aggregating the data into hexagonal bins for spatial analysis. The color gradient, ranging from light yellow to deep purple, represents the density of theft incidents, where darker shades indicating higher densities. A prominent "High Theft Area" is highlighted with a red-bordered white label and an arrow pointing to the hexagonal bin with the highest density. Hexagons were chosen because of their aesthetic and analytical advantages, such as uniform adjacency and equal distance between centroids.For this map, I want to inform people the theft hot spot in Philadelphia and inspire public safety discussion.

# 11/19 Day 18 Topography

```{r}
library(sf)
library(plotly)
```


```{r}
buildings <- st_read("/Users/luoxiaoyi/Desktop/2024 Fall/communication/30daysChallenge/30DayMapChallenge/LI_BUILDING_FOOTPRINTS/LI_BUILDING_FOOTPRINTS.shp") %>%
  st_transform(crs = 4326)
```
```{r}
buildings <- st_make_valid(buildings)

invalid_geometries <- sum(!st_is_valid(buildings))
if (invalid_geometries > 0) {
  cat("There are still", invalid_geometries, "invalid geometries.\n")
} else {
  cat("All geometries are valid!\n")
}
```


```{r}

buildings <- buildings %>%
  mutate(absolute_height = BASE_ELEVA + APPROX_HGT)

building_points <- st_centroid(buildings)

data <- st_coordinates(building_points) %>%
  as.data.frame() %>%
  mutate(height = buildings$absolute_height)

plot_ly(
  data,
  x = ~X, y = ~Y, z = ~height,
  type = "scatter3d", mode = "markers",
  marker = list(size = 3, color = ~height, colorscale = "Viridis", opacity = 0.8)
) %>%
  layout(
    title = "Philadelphia Building Heights",
    scene = list(
      xaxis = list(title = "Longitude"),
      yaxis = list(title = "Latitude"),
      zaxis = list(title = "Height")
    )
  )
```
This 3D scatter plot illustrates the height distribution of buildings in Philadelphia. The data combines BASE_ELEVATION and APPROX_HGT to represent the total height of each building. The x- and y-axes denote the spatial coordinates (longitude and latitude), while the z-axis captures the total height. A 3D perspective was chosen to effectively visualize the spatial distribution and varying heights of buildings. The clustering of taller buildings demonstrates urban density and potential areas of economic or business activity. This map could be used for urban planning, zoning assessments, or real estate analysis.

# 11/20 Day 12 Time and Space

```{r}
library(tidycensus)
library(tidyverse)
library(ggiraph)
library(patchwork)
```

```{r}
income_2010 <- get_acs(
  geography = "county",
  variables = "B19013_001",
  state = "PA",
  year = 2010,
  geometry = TRUE
) %>% 
  rename(income_2010 = estimate)

income_2020 <- get_acs(
  geography = "county",
  variables = "B19013_001",
  state = "PA",
  year = 2020,
  geometry = TRUE
) %>% 
  rename(income_2020 = estimate)

income_change <- income_2020 %>%
  st_drop_geometry() %>%
  select(GEOID, NAME, income_2020) %>%
  left_join(income_2010 %>% st_drop_geometry() %>% select(GEOID, income_2010), by = "GEOID") %>%
  mutate(
    pct_change = (income_2020 - income_2010) / income_2010 * 100,
    NAME = str_remove(NAME, " County, Pennsylvania")
  ) %>%
  left_join(income_2020 %>% select(GEOID, geometry), by = "GEOID") %>%
  st_as_sf()

income_state <- map_dfr(2010:2020, function(year) {
  get_acs(
    geography = "state",
    variables = "B19013_001",
    state = "PA",
    year = year
  ) %>%
    mutate(year = year)
})
```

```{r}
map_panel <- ggplot(income_change, aes(fill = pct_change)) + 
  geom_sf_interactive(aes(data_id = GEOID)) + 
  scale_fill_distiller(palette = "RdYlGn", direction = 1, name = "Change (%)") + 
  theme_void() +
  labs(
    title = "Change in Median Household Income (2010-2020)",
    subtitle = "By county in Pennsylvania",
    fill = "Percent Change"
  )

plot_panel <- ggplot(income_state, aes(x = year, y = estimate)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "blue", size = 2) +
  scale_y_continuous(labels = scales::label_dollar()) +
  labs(
    title = "Median Household Income Trend (2010-2020)",
    x = "Year",
    y = "Median Household Income",
    caption = "Data source: ACS"
  ) +
  theme_minimal(base_size = 14)

combined_plot <- girafe(
  ggobj = map_panel + plot_panel,
  width_svg = 10,
  height_svg = 5
) %>%
  girafe_options(opts_hover(css = "fill:cyan;"))

combined_plot
```

I combined spatial and temporal data to indicate the income change over space and time in Pennsylvania. The spatial change map highlights the percentage change in median household income (2010-2020) for each county in Pennsylvania. Counties with extreme changes are prominently visible through stark colors, helping viewers identify key areas quickly. In addition, the temporal trend plot illustrates the overall median household income trend for Pennsylvania from 2010 to 2020. These two visualization together can help identify counties where targeted economic policies might be needed based on negative or stagnant growth.


# 11/21 Day 24 Only Circular Shapes

```{r}
library(tidycensus)
library(sf)
library(dplyr)
library(ggplot2)
```

```{r}
philly_census <- get_acs(
  geography = "block group",
  variables = "B01003_001E", 
  state = "PA",
  county = "Philadelphia",
  year = 2019,
  geometry = TRUE
)

philly_census <- philly_census %>%
  mutate(
    area_km2 = as.numeric(st_area(geometry)) / 1e6, 
    pop_density = estimate / area_km2  
  )

philly_centroids <- st_centroid(philly_census)

philly_centroids_df <- as.data.frame(st_coordinates(philly_centroids)) %>%
  bind_cols(philly_census %>% st_drop_geometry())

```

```{r}
ggplot() +
  geom_sf(data = philly_census, fill = "grey90", color = "white") + 
  geom_point(data = philly_centroids_df,
             aes(x = X, y = Y, size = pop_density, color = pop_density),
             alpha = 0.7) +
  scale_size_continuous(range = c(1, 8), name = "Pop Density\n(people/km²)") +
  scale_color_viridis_c(option = "plasma", name = "Pop Density\n(people/km²)", direction = -1) +
  labs(
    title = "Population Density in Philadelphia",
    subtitle = "Block Group Centroids Represented by Circles",
    caption = "Data source: 2019 ACS via tidycensus"
  ) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14, face = "italic"),
    plot.caption = element_text(size = 10),
    legend.position = "right"
  )
```
For this map, I want to visualize population density across Philadelphia, and I used circular markers placed at the centroids of census block groups. The size and color of the circles correspond to the population density (in people per square kilometer), yellow for low density to dark purple for high density. This design allows for a clear spatial representation of densely populated areas. By encoding population density through two visual dimensions (size and color), viewers can quickly identify patterns and compare block groups.


# 11/22 Day 22 2 Color

```{r}
library(tidycensus)
library(ggplot2)
library(sf)
library(dplyr)
library(tigris)
```

```{r}
housing_vars <- c(
  owner_occupied = "B25003_002E", 
  renter_occupied = "B25003_003E",
  total_housing = "B25001_001E"
)

philly_housing <- get_acs(
  geography = "tract",
  variables = housing_vars,
  state = "PA",
  county = "Philadelphia",
  geometry = TRUE
)

philly_housing <- philly_housing %>%
  select(GEOID, NAME, variable, estimate, geometry) %>%
  pivot_wider(names_from = variable, values_from = estimate, names_prefix = "") %>%
  mutate(
    owner_occupied = B25003_002,
    renter_occupied = B25003_003,
    total_housing = B25001_001
  )

philly_housing <- philly_housing %>%
  group_by(GEOID) %>%
  mutate(
    total_housing = owner_occupied + renter_occupied,
    owner_pct = owner_occupied / total_housing,
    renter_pct = renter_occupied / total_housing
  )
```

```{r}
philly_housing <- philly_housing %>%
  mutate(
    dominance = renter_pct - owner_pct, 
    dominance_category = case_when(
      dominance > 0 ~ "Rentership > Ownership",
      dominance <= 0 ~ "Ownership > Rentership"
    )
  )

philly_housing <- philly_housing %>%
  drop_na()
```


```{r}
ggplot(philly_housing) +
  geom_sf(data = philly_census, fill = "grey90", color = "white") + 
  geom_sf(aes(fill = dominance_category), color = NA) +
  scale_fill_manual(
    values = c("Rentership > Ownership" = "blue", "Ownership > Rentership" = "orange"),
    name = "Housing Dominance"
  ) +
  labs(
    title = "Ownership vs Rentership Dominance in Philadelphia",
    subtitle = "Comparison of Housing Tenure by Census Tract",
    caption = "Data Source: ACS 2019 5-Year Estimates"
  ) +
  theme_minimal() +
    theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank()
    )
```

The map illustrates the housing tenure dominance in Philadelphia at the census tract level. I want to highlight whether ownership or rentership is the prevailing housing type in different parts of the city. Each tract is colored based on the comparison of the proportion of owner-occupied housing units versus renter-occupied housing units. Orange areas represent tracts where ownership is greater than rentership and blue areas represent tracts where rentership is greater than ownership. This map helps identify areas where housing policies might focus on rental housing affordability or increasing homeownership opportunities. 
















